---
title: "zmisc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{zmisc}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# We need rprojroot to locate other files needed for the Vignette
library(rprojroot)

# Source a few helper/utility functions
source(find_package_root_file("vignettes","utils_knitr.R"))
source(find_package_root_file("vignettes","utils_roxygen.R"))

# Get roxygen blocks, use force to trigger any warnings immediately
blocks <- roxy_get_blocks(find_package_root_file())
blocks <- force(blocks)

```

## `r desc::desc_get("Title")`

`r desc::desc_get("Description")`

## Installation

You can install the released version of `zmisc` from [CRAN](https://cran.r-project.org/package=zmisc) with:

```r
install.packages("zmisc")
```

You can install the development version of `zmisc` from [GitHub](https://github.com/torfason/zmisc) with:

```r
remotes::install_github("torfason/zmisc")
```

## Usage

In order to use the package, you generally want to attach it first:

```{r load_package}
library(zmisc)
```

## Quick and easy value lookups

The functions [lookup()] and [lookuper()] are used to look up values from a lookup
table, which can be supplied as a `vector`, a `list`, or a `data.frame`. The functions
are in some ways similar to the Excel function `VLOOKUP()`, but are designed to work smoothly 
in an R workflow, in particular within pipes.

### lookup: `r roxy_get_section(blocks, "lookup", "title")`

`r roxy_get_section(blocks, "lookup", "description")`

#### Examples

```{r, echo=FALSE}
roxy_get_section(blocks, "lookup", "examples") |> kat_code()
```

### lookuper: `r roxy_get_section(blocks, "lookuper", "title")`

`r roxy_get_section(blocks, "lookuper", "description")`

#### Examples

```{r, echo=FALSE}
roxy_get_section(blocks, "lookuper", "examples") |> kat_code()
```

## Safer sampling, sequencing and aggregation

The functions [zample()], [zeq()], and [zingle()] are intended to make your code
less likely to break in mysterious ways when you encounter unexpected boundary
conditions. The [zample()] and [zeq()] are almost identical to the [sample()]
and [seq()] functions, but a bit safer.

### zample: `r roxy_get_section(blocks, "zample", "title")`

`r roxy_get_section(blocks, "zample", "description")`

#### Examples

```{r, echo=FALSE}
roxy_get_section(blocks, "zample", "examples") |> kat_code()
```


### zeq: `r roxy_get_section(blocks, "zeq", "title")`

`r roxy_get_section(blocks, "zeq", "description")`

#### Examples

```{r, echo=FALSE}
roxy_get_section(blocks, "zeq", "examples") |> kat_code()
```


### zingle: `r roxy_get_section(blocks, "zingle", "title")`

`r roxy_get_section(blocks, "zingle", "description")`

#### Examples

```{r, echo=FALSE}
roxy_get_section(blocks, "zingle", "examples") |> kat_code()
```


[lookup()]: https://torfason.github.io/zmisc/reference/lookup.html
[lookuper()]: https://torfason.github.io/zmisc/reference/lookuper.html

[zeq()]: https://torfason.github.io/zmisc/reference/zeq.html
[zample()]: https://torfason.github.io/zmisc/reference/zample.html
[zingle()]: https://torfason.github.io/zmisc/reference/zingle.html

[seq()]:    https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/seq
[sample()]: https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sample
